---
title: "LAb5"
author: "Alain Brou"
date: "10/26/2020"
output: html_document
---

Build on the previous lab in creating useful models.

Concentrate on a smaller subset than previous. For instance if you wanted to look at wages for Hispanic women with at least a college degree, you might use

```{r}
attach(acs2017_ny)
use_varb <- (AGE >= 25) & (AGE <= 55) & (LABFORCE == 2) & (WKSWORK2 > 4) & (UHRSWORK >= 35) & (AfAm == 1) & (female==1) & ((educ_college == 1) | (educ_advdeg == 1))
dat_use <- subset(acs2017_ny,use_varb) # 
detach()

```


```{r}
mod2<- lm((INCWAGE ~ AGE + I(AGE^2) +FAMSIZE +I(FAMSIZE^2)+ I(FAMSIZE^3)))

summary(mod2)
```

```{r}
NNobserv<-length(INCWAGE)
set.seed(123456)
graph_observ<-(runif(NNobserv)<0.1)
data_to_graph<-subset(dat_use,graph_observ)
plot(INCWAGE ~ jitter(AGE, factor = 2), pch = 16, col = rgb(0.5, 0.5, 0.5, alpha = 0.2), data = dat_use)
# ^^ that looks like crap since Wages are soooooooo skew!  So try to find some sensible ylim = c(0, ??)
plot(INCWAGE ~ jitter(AGE, factor = 2), pch = 16, col = rgb(0.5, 0.5, 0.5, alpha = 0.2), ylim = c(0,150000), data = dat_use)

```

```{r}
mod3<- lm((INCWAGE ~ AGE + I(AGE^2) + I(AGE^3) + educ_college +educ_advdeg+FAMSIZE +I(FAMSIZE^2)+ I(FAMSIZE^3)))

mod4<-lm((INCWAGE ~ AGE + I(AGE^2) +I(AGE^3)+I(AGE^4)+ educ_college +educ_advdeg+FAMSIZE +I(FAMSIZE^2)+ I(FAMSIZE^3)))

mod5<-lm((INCWAGE ~ AGE + I(AGE^2) +I(AGE^3)+I(AGE^4)+ educ_college))

summary(mod3)
summary(mod4)
summary(mod5)
```
when the log^2(AGE) is used, the comparison of these types is not implemented, however the log(AGE) works.
we also note that the higher order of the polynomials of AGE, the coeffcients or estimates decrease but stay stastically significant as in the mod4

Also adding a dummy variable as educ_college, it makes the varibale AGE insignificant statiscally.

we do not use polynomials on dummy variables because the no matter the order we still get the same number, etither o or 1 .



```{r}
library("AER")
Im<-lm(INCWAGE ~ log(AGE) + female + I(female*AGE) + I(female*(AGE^2)+I(female*(AGE^3))+educ_college +educ_advdeg+FAMSIZE +I(FAMSIZE^2)+ I(FAMSIZE^3))) 
Im2<-lm(log1p(INCWAGE) ~ AGE  + female + I(female*AGE) + I(female*(AGE^2)+I(female*(AGE^3))+educ_college +educ_advdeg+FAMSIZE +I(FAMSIZE^2)+ I(FAMSIZE^3)))
summary(Im)
graph_observ<-(runif(NNobserv)<0.1)
data_to_graph<-subset(dat_use,graph_observ)
plot(INCWAGE ~ jitter(AGE, factor = 2), pch = 16, col = rgb(0.5, 0.5, 0.5, alpha = 0.2), data = dat_use)
# ^^ that looks like crap since Wages are soooooooo skew!  So try to find some sensible ylim = c(0, ??)
plot(INCWAGE ~ jitter(AGE, factor = 2), pch = 16, col = rgb(0.5, 0.5, 0.5, alpha = 0.2), ylim = c(0,150000), data = dat_use)
modPredict<-data.frame(AGE= 25:55, female = 1, AfAm=1,FAMSIZE=1,educ_nohs=1,educ_college = 0, educ_advdeg= 0)
modPredict$yhat<- predict(mod4, newdata = modPredict)
summary(modPredict)
lines(yhat~AGE,data= modPredict)
lines(yhat~FAMSIZE,data= modPredict)
```
